Should geophysicists use the gravity disturbance or the anomaly?

### 2018-05-30 manuscript/letter.tex
change authors order
small correction

\author[Oliveira Jr et al.]{
\parbox{\linewidth}{%
    Vanderlei C. Oliveira Jr$^1$\thanks{Email: vanderlei@on.br},
    Leonardo Uieda$^2$, Val\'{e}ria C. F. Barbosa$^1$, and
    \linebreak Kristoffer A. T. Hallam$^{1}$
    \vspace{0.3cm}
}%
    \\
    $^1$ Department of Geophysics, Observat\'{o}rio Nacional, Rio de Janeiro, Brazil \\
    $^2$ Department of Geology and Geophysics, SOEST, University of Hawai'i at M\={a}noa, Honolulu, USA
}

@@

Although the gravity disturbance is well-known in geodesy,
its use in applied geophysics is uncommon.
For years, geophysicists have been using gravity anomalies for modelling
the gravitational effects of geological bodies.
Wether geophysicists should use the gravity anomaly or the gravity disturbance
is of more than mere academic interest.
It is a question that underpins the very assumptions about what it is that we
are actually modelling.

>>>>

\author[Oliveira Jr et al.]{
\parbox{\linewidth}{%
    Vanderlei C. Oliveira Jr$^1$\thanks{Email: vanderlei@on.br},
    Leonardo Uieda$^2$, Kristoffer A. T. Hallam$^{1}$ and
    \linebreak Val\'{e}ria C. F. Barbosa$^1$
    \vspace{0.3cm} }%
    \\
    $^1$ Department of Geophysics, Observat\'{o}rio Nacional, Rio de Janeiro, Brazil \\
    $^2$ Department of Geology and Geophysics, SOEST, University of Hawai'i at M\={a}noa, Honolulu, USA
}

@@

Although the gravity disturbance is well-known in geodesy,
its use in applied geophysics is uncommon.
For years, geophysicists have been using gravity anomalies for modelling
the gravitational effects of geological bodies.
Whether geophysicists should use the gravity anomaly or the gravity disturbance
is of more than mere academic interest.
It is a question that underpins the very assumptions about what it is that we
are actually modelling.
